---
title: "Key Word in Context app"
author: "cmo"
date: "05/06/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Build a Key-word-in-context application

As we have seen, the sentiment results and the lexical dispersion plot only generate more questions about the text (which is a good thing). Of course these computational approaches should inevtibaly lead us back to closely reading the text, but even in that endeavour we can solicit the aid of R by creating a key-word-in-context search. Let's undertake a key-word-in-context search of Moby-Dick.

```{r}
setwd("~/Desktop/git-space/hacking-moby-dick/")
library(dplyr)

input.dir <- "texts/" #notice here that I migrated my moby-dick.txt into a sub-directory called "texts" for ease of processing and organization
file.v <- dir(input.dir, "moby-dick.txt")
file.v

# Function takes a vector of file names and a directory path and
# returns a list in which each item in the list is an ordered
# vector of words from one of the files in the vector of file names 

make.file.word.v.l <- function(file.v, input.dir){
  text.word.vector.l <- list()
  # loop over the files
  for(i in 1:length(file.v)){
    # read the file in (notice that it is here that we need to know the input # directory
    text.v <- scan(paste(input.dir, file.v[i], sep="/"),
                   what="character", sep="\n") #convert to single string
    text.v <- paste(text.v, collapse=" ")
    #lowercase and split on non-word characters
    text.lower.v <- tolower(text.v)
    text.words.v <- strsplit(text.lower.v, "\\W")
    text.words.v <- unlist(text.words.v)
    #remove the blanks
    text.words.v <- text.words.v[which(text.words.v!="")]
    #use the index id from the files.v vector as the "name" in the list 
    text.word.vector.l[[file.v[i]]] <- text.words.v
  }
  return(text.word.vector.l)
}
# call the function with file.v and input.dir, put into new variable
my.corpus.l <- make.file.word.v.l(file.v, input.dir)
#show the first 100 words of the corpus
my.corpus.l[[1]][1:100]
```

I have run a complicated for-loop that iterates over the words in the text file, separates them properly, and puts them in a vector (an ordered list). Now we can simply create new vectors that seek out a search term.

```{r}
#search and find positions of word
great.positions.v <- which(my.corpus.l[[1]][]=="great")
great.positions.v
```
This might look intimidating, but this shows you exactly in what position in the list these terms are occuring.

```{r}
great.context <- great.positions.v
context <- 4
results <- for(i in 1:length(great.context)){
  start <- great.context[i]-context
  end <- great.context[i]+context
  before <- my.corpus.l[[1]][start:(start+context-1)]
  after <- my.corpus.l[[1]][(start+context+1) :end]
  keyword <- my.corpus.l[[1]][start+context]
  cat("----------", i, "----------", "\n")
  cat(before,"[",keyword, "]", after, "\n")
}
```

Suppose we want to combine terms with great---say, with some other negative terms from the sentiment analysis.

```{r}
death.positions.v <- which(my.corpus.l[[1]][]=="death")
dead.positions.v <- which(my.corpus.l[[1]][]=="dead")
dark.positions.v <- which(my.corpus.l[[1]][]=="dark")
# now combine the three search-placement vectors into one wit the 'c' combine function
dark.words.md <- (c(death.positions.v, dead.positions.v, dark.positions.v))

dark.words.context <- dark.words.md
context <- 4 # here you can adjust the context
results <- for(i in 1:length(dark.words.context)){
  start <- dark.words.context[i]-context
  end <- dark.words.context[i]+context
  before <- my.corpus.l[[1]][start:(start+context-1)]
  after <- my.corpus.l[[1]][(start+context+1) :end]
  keyword <- my.corpus.l[[1]][start+context]
  cat("----------", i, "----------", "\n")
  cat(before,"[",keyword, "]", after, "\n")
}
```
What if you want to identify the first instance of "death"?

```{r}
first.death <- death.positions.v[1]
my.corpus.l[[1]][first.death]
#grab words before and after 1st 'death' instances and use cat to pretty print
cat(my.corpus.l[[1]] [(first.death-2):(first.death+2)])
```

```{r}
# What about the last 'death'?
last.death <- last(death.positions.v)
my.corpus.l[[1]][last.death]
cat(my.corpus.l[[1]] [(last.death-2):(last.death+2)])
```

Now for the fun part. Copy and paste this code block into RStudio. You should be able to run your own key-word-search-in-context application.
```
# This creates a function to take a list containing word vector # from text files and allows for interactive user input to produce KWIC lists 
doitKwic <- function(named.text.word.vector.l){
show.files(names(named.text.word.vector.l)) 
  # ask the user for three bits of information 
  file.id <- as.numeric(readline(
"Which file would you like to examine? Enter a file number: \n")) 
  context <- as.numeric(readline(
  "How much context do you want to see? Enter a number: \n")) 
  keyword <- tolower((readline("Enter a keyword: \n")))
  hits.v <- which(named.text.word.vector.l[[file.id]] == keyword) 
  if(length(hits.v)>0){
    result <- NULL
    for(h in 1:length(hits.v)){
      start <- hits.v[h]-context
      if(start < 1){
        start <- 1 }
      end <- hits.v[h]+context
      cat("\n-----------------------", h, "-------------------------\n") 
      cat(named.text.word.vector.l[[file.id]][start:(hits.v[h]-1)], sep=" ") 
      cat(" [", named.text.word.vector.l[[file.id]][hits.v[h]],"] ", sep="") 
      cat(named.text.word.vector.l[[file.id]][(hits.v[h]+1):end], sep=" ")
      myrow <- cbind(hits.v[h], 
          paste(named.text.word.vector.l[[file.id]][start:(hits.v[h]-1)],
                                      collapse=" "), 
          paste(named.text.word.vector.l[[file.id]][hits.v[h]],
                                      collapse=" "), 
          paste(named.text.word.vector.l[[file.id]][(hits.v[h]+1):end],
                                      collapse=" "))
      result <- rbind(result,myrow)
    }
    colnames(result) <- c("position", "left", "keyword", "right") 
    toprint <- as.numeric((
      readline("Would you like to save this result to a file: enter 1=yes or 0=no \n")))
    if(toprint==1){
      write.csv(result,
                paste("search-results/", keyword,"_In_",
                      context, names(named.text.word.vector.l)[file.id], ".csv", sep="")) 
      }
  } else {
    cat("YOUR KEYWORD WAS NOT FOUND\n")
  }
}

doitKwic(my.corpus.l)
```
It will first ask for a file number. Since there is only one file number, enter '1'.

It will then ask for how much context you would like. I enter '4'.

Then, if we enter a term from our sentiment list, 'grand', the results are:

----------------------- 1 -------------------------
a sea ibid the [mighty] whales which swim in

----------------------- 2 -------------------------
whale boat suddenly a [mighty] mass emerged from the

----------------------- 3 -------------------------
euroclydon nevertheless is a [mighty] pleasant zephyr to any

----------------------- 4 -------------------------
good laugh is a [mighty] good thing and rather

----------------------- 5 -------------------------
smallest strands in the [mighty] cable of the scriptures

----------------------- 6 -------------------------
far rush of the [mighty] whale which even now

----------------------- 7 -------------------------
this struck me as [mighty] singular yet upon second

----------------------- 8 -------------------------
nation s census a [mighty] pageant creature formed for

----------------------- 9 -------------------------
bildad might have a [mighty] deal to say about

----------------------- 10 -------------------------
than the high and [mighty] business of whaling one

----------------------- 11 -------------------------
mother of that now [mighty] colony moreover in the

----------------------- 12 -------------------------
our leviathan who but [mighty] job and who composed

----------------------- 13 -------------------------
in one of the [mighty] triumphs given to a

----------------------- 14 -------------------------
of an enraged and [mighty] man but were the

----------------------- 15 -------------------------
who in all thy [mighty] earthly marchings ever cullest

----------------------- 16 -------------------------
overbearing dignity of some [mighty] woe ere long from

----------------------- 17 -------------------------
and there s a [mighty] difference between a living

----------------------- 18 -------------------------
a leech till the [mighty] brute is worried to

----------------------- 19 -------------------------
of the high and [mighty] cabin in strange contrast

----------------------- 20 -------------------------
for a parmacetty and [mighty] quick captain ahab and

----------------------- 21 -------------------------
pregnant with many a [mighty] birth no wonder then

----------------------- 22 -------------------------
and fearless as this [mighty] steed whether marching amid

----------------------- 23 -------------------------
to preserve all his [mighty] swells and undulations and

----------------------- 24 -------------------------
the assault yes a [mighty] change had come over

----------------------- 25 -------------------------
hoary with mosses speak [mighty] head and tell us

----------------------- 26 -------------------------
in thinking how this [mighty] monster is actually a

----------------------- 27 -------------------------
leviathan is of so [mighty] a magnitude all his

----------------------- 28 -------------------------
whale this high and [mighty] god like dignity inherent

----------------------- 29 -------------------------
all things that are [mighty] wears a false brow

----------------------- 30 -------------------------
his men in a [mighty] rage that was a

----------------------- 31 -------------------------
drawn off from some [mighty] fountain and with half

----------------------- 32 -------------------------
our conceit of the [mighty] misty monster to behold

----------------------- 33 -------------------------
more i consider this [mighty] tail the more do

----------------------- 34 -------------------------
dark valley between three [mighty] heaven abiding peaks that

----------------------- 35 -------------------------
hummed around him the [mighty] idler seemed the cunning

----------------------- 36 -------------------------
its length was the [mighty] circular basket of ribs

----------------------- 37 -------------------------
fossil whale from his [mighty] bulk the whale affords

----------------------- 38 -------------------------
bulk to produce a [mighty] book you must choose

----------------------- 39 -------------------------
you must choose a [mighty] theme no great and

----------------------- 40 -------------------------
i stand among these [mighty] leviathan skeletons skulls tusks

----------------------- 41 -------------------------
mark thou high and [mighty] pilot thou tellest me

----------------------- 42 -------------------------
listen what s the [mighty] difference between holding a

----------------------- 43 -------------------------
long slow billows of [mighty] bulk and striving in

----------------------- 44 -------------------------
the bottomless blue rushed [mighty] leviathans sword fish and

----------------------- 45 -------------------------
a gentle joyousness a [mighty] mildness of repose in

----------------------- 46 -------------------------
land and as the [mighty] iron leviathan of the

----------------------- 47 -------------------------
almost simultaneously with a [mighty] volition of ungraduated instantaneous


----

This is adapted from Matthew Jockers's [*Text Analysis in R for Students of Literature*](http://www.matthewjockers.net/text-analysis-with-r-for-students-of-literature/) (2014).

Return to [Week 8](https://cmohge1.github.io/hacking-moby-dick/week_8_discussion.html)
