---
title: "Create a lexical dispersion plot"
author: "cmo"
date: "6/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create a lexical dispersion plot based on the sentiment word results

First you need set your working directory (for me, that is setwd("~/git-space/ranalysis/texts/")). 

Then you load two libraries:

library("rJava")

library("qdap")

```{r include=FALSE}

setwd("~/git-space/hacking-moby-dick/")
library("rJava")
library("qdap")
```

Next you will prepare the text, making sure all of the charcater encoding is uniform.

```{r}
md.text <- scan("moby-dick.txt", what = "characters", sep = "\n")
md.text <- iconv(md.text, "latin1", "ASCII", "")
md.text <- paste(md.text, collapse = c(" ", "\n"))
md.text.prep <- qprep(md.text)
md.text.prep <- replace_contraction(md.text)
md.text.stripped <- strip(md.text.prep, char.keep = c("?", "."))
```
```{r}
dispersion_plot(md.text, c("poor", "strange", "dead", "death", "whale", "ahab", "great", "well", "good", "right", "best", "work"),
                color = "black", bg.color = "grey90", horiz.color = "grey85",
                total.color = "black", symbol = "|", title = "Lexical Dispersion Plot in Moby-Dick",
                rev.factor = TRUE, wrap = "'", xlab = NULL, ylab = "Word Frequencies",
                size = 4, plot = TRUE)
```

What kinds of questions can you generate from the placement of these words?

Now try to change the search terms.
